# MI500: Multi-path exploration results

Here we present the results for the **best performances** and **activation gene coverage** generated by each selection scheme replicate on the multi-path exploration diagnostic.
Best performance found refers to the largest average trait score found in a given population.
Note that activation gene coverage values are gathered at the population-level.
Activation gene coverage refers to the count of unique activation genes in a given population; this gives us a range of integers between 0 and 100.

## Analysis dependencies

```{r base-mpe-libs, message=FALSE}
library(ggplot2)
library(cowplot)
library(dplyr)
library(PupillometryR)
```

## Data

```{r int-con-data, message=FALSE}
base   = filter(base_over_time,   Diagnostic == 'MULTIPATH_EXPLORATION' & Structure == 'IS')
mi50   = filter(mi50_over_time,   Diagnostic == 'MULTIPATH_EXPLORATION' & Structure == 'IS')
mi5000 = filter(mi5000_over_time, Diagnostic == 'MULTIPATH_EXPLORATION' & Structure == 'IS')

base$Interval = '500'
mi50$Interval = '50'
mi5000$Interval = '5000'

df_ot = rbind(base, mi50, mi5000)
df_ot$Interval = factor(df_ot$Interval, levels=c('50','500','5000'))

base = filter(base_best,     Diagnostic == 'MULTIPATH_EXPLORATION' & Structure == 'IS')
mi50 = filter(mi50_best,     Diagnostic == 'MULTIPATH_EXPLORATION' & Structure == 'IS')
mi5000 = filter(mi5000_best, Diagnostic == 'MULTIPATH_EXPLORATION' & Structure == 'IS')

base$Interval = '500'
mi50$Interval = '50'
mi5000$Interval = '5000'

df_best = rbind(mi50,base,mi5000)
df_best$Interval = factor(df_best$Interval, levels = c('50','500','5000'))
```

## Truncation selection

Here we analyze how the different population structures affect truncation selection (size 8) on the contradictory objectives diagnostic.

### Performance

#### Performance over time

```{r base-tru-mpe-perf, message=FALSE}
lines = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TRUNCATION') %>%
  group_by(Interval, Generations) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )
ggplot(lines, aes(x=Generations, y=mean, group = Interval, fill = Interval, color = Interval, shape = Interval)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, Generations %% 2000 == 0), size = 2.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle("Performance over time") +
  p_theme
```

#### Best performance

Best performancefound throughout the 50,000 generations.

```{r base-tru-mpe-per-bst, warning=FALSE}
filter(df_best, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TRUNCATION' & VAR == 'pop_fit_max') %>%
  ggplot(., aes(x = Interval, y = VAL / DIMENSIONALITY, color = Interval, fill = Interval, shape = Interval)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_discrete(
    name="Interval"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi, ) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Best performance')+
  p_theme + coord_flip()
```

##### Stats

Summary statistics for the first generation a best performance found.

```{r base-tru-mpe-per-bst-sum}
performance = filter(df_best, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TRUNCATION' & VAR == 'pop_fit_max')
performance %>%
  group_by(Interval) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(VAL)),
    min = min(VAL, na.rm = TRUE) / DIMENSIONALITY,
    median = median(VAL, na.rm = TRUE) / DIMENSIONALITY,
    mean = mean(VAL, na.rm = TRUE) / DIMENSIONALITY,
    max = max(VAL, na.rm = TRUE) / DIMENSIONALITY,
    IQR = IQR(VAL, na.rm = TRUE) / DIMENSIONALITY
  )
```

Kruskal–Wallis test provides evidence of difference among selection schemes.

```{r base-tru-mpe-per-bst-kru}
kruskal.test(VAL ~ Interval, data = performance)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r base-tru-mpe-per-bst-wil}
pairwise.wilcox.test(x = performance$VAL, g = performance$Interval, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'g')
```

#### Final performance

Best performance is found throughout in final generation.

```{r base-tru-mpe-per-end, warning=FALSE}
filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TRUNCATION' & Generations == 50000) %>%
  ggplot(., aes(x = Interval, y = pop_fit_max / DIMENSIONALITY, color = Interval, fill = Interval, shape = Interval)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_discrete(
    name="Interval"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi, ) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Final performance')+
  p_theme + coord_flip()
```

##### Stats

Summary statistics for the best performance is found in final generation.

```{r base-tru-mpe-per-end-sum}
performance = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TRUNCATION' & Generations == 50000)
performance %>%
  group_by(Interval) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_fit_max)),
    min = min(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    median = median(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    max = max(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(pop_fit_max / DIMENSIONALITY, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among selection schemes.

```{r base-tru-mpe-per-end-kru}
kruskal.test(pop_fit_max ~ Interval, data = performance)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r base-tru-mpe-per-end-wil}
pairwise.wilcox.test(x = performance$pop_fit_max, g = performance$Interval, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'g')
```

### Activation gene coverage

Activation gene coverage analysis.

#### Coverage over time

Activation gene coverage over time.

```{r base-mpe-act-tru-ot, warning=FALSE}
# data for lines and shading on plots
lines = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TRUNCATION') %>%
  group_by(Interval, Generations) %>%
  dplyr::summarise(
    min = min(pop_act_cov),
    mean = mean(pop_act_cov),
    max = max(pop_act_cov)
  )
ggplot(lines, aes(x=Generations, y=mean, group = Interval, fill = Interval, color = Interval, shape = Interval)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, Generations %% 2000 == 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Activation gene coverage over time')+
  p_theme
```

#### End of 50,000 generations

Activation gene coverage in the population at the end of 50,000 generations.

```{r base-mpe-act-tru-end}
### end of run
filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TRUNCATION' & Generations == 50000) %>%
  ggplot(., aes(x = Interval, y = pop_act_cov, color = Interval, fill = Interval, shape = Interval)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.3) +
  geom_point(position = position_jitter(height = .05, width = .05), size = 1.5, alpha = 0.5) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_shape_manual(values=SHAPE)+
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_discrete(
    name="Interval"
  ) +
  scale_colour_manual(values = cb_palette_mi) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Final activation gene coverage')+
  p_theme + coord_flip()
```

##### Stats

Summary statistics for activation gene coverage.

```{r base-mpe-act-tru-end-sum}
coverage = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TRUNCATION' & Generations == 50000)
coverage %>%
  group_by(Interval) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_act_cov)),
    min = min(pop_act_cov, na.rm = TRUE),
    median = median(pop_act_cov, na.rm = TRUE),
    mean = mean(pop_act_cov, na.rm = TRUE),
    max = max(pop_act_cov, na.rm = TRUE),
    IQR = IQR(pop_act_cov, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of no difference among activation gene coverage.
```{r base-mpe-act-tru-end-kru}
kruskal.test(pop_act_cov ~ Interval, data = coverage)
```


## Tournament selection

Here we analyze how the different population structures affect tournament selection (size 8) on the contradictory objectives diagnostic.

### Performance

#### Performance over time

```{r base-tor-mpe-perf, message=FALSE}
lines = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TOURNAMENT') %>%
  group_by(Interval, Generations) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )
ggplot(lines, aes(x=Generations, y=mean, group = Interval, fill = Interval, color = Interval, shape = Interval)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, Generations %% 2000 == 0), size = 2.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle("Performance over time") +
  p_theme
```

#### Best performance

Best performance is found throughout the 50,000 generations.

```{r base-tor-mpe-per-bst, warning=FALSE}
filter(df_best, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TOURNAMENT' & VAR == 'pop_fit_max') %>%
  ggplot(., aes(x = Interval, y = VAL / DIMENSIONALITY, color = Interval, fill = Interval, shape = Interval)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_discrete(
    name="Interval"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi, ) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Best performance')+
  p_theme + coord_flip()
```

##### Stats

Summary statistics for the best performance found.

```{r base-tor-mpe-per-bst-sum}
performance = filter(df_best, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TOURNAMENT' & VAR == 'pop_fit_max')
performance %>%
  group_by(Interval) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(VAL)),
    min = min(VAL, na.rm = TRUE) / DIMENSIONALITY,
    median = median(VAL, na.rm = TRUE) / DIMENSIONALITY,
    mean = mean(VAL, na.rm = TRUE) / DIMENSIONALITY,
    max = max(VAL, na.rm = TRUE) / DIMENSIONALITY,
    IQR = IQR(VAL, na.rm = TRUE) / DIMENSIONALITY
  )
```

Kruskal–Wallis test provides evidence of difference among selection schemes.

```{r base-tor-mpe-per-bst-kru}
kruskal.test(VAL ~ Interval, data = performance)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r base-tor-mpe-per-bst-wil}
pairwise.wilcox.test(x = performance$VAL, g = performance$Interval, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'g')
```

#### Final performance

Best performance is found in final generation.

```{r base-tor-mpe-per-end, warning=FALSE}
filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TOURNAMENT' & Generations == 50000) %>%
  ggplot(., aes(x = Interval, y = pop_fit_max / DIMENSIONALITY, color = Interval, fill = Interval, shape = Interval)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_discrete(
    name="Interval"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi, ) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Final performance')+
  p_theme + coord_flip()
```

##### Stats

Summary statistics for best performance is found in final generation.

```{r base-tor-mpe-per-end-sum}
performance = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TOURNAMENT' & Generations == 50000)
performance %>%
  group_by(Interval) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_fit_max)),
    min = min(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    median = median(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    max = max(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(pop_fit_max / DIMENSIONALITY, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among selection schemes.

```{r base-tor-mpe-per-end-kru}
kruskal.test(pop_fit_max ~ Interval, data = performance)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r base-tor-mpe-per-end-wil}
pairwise.wilcox.test(x = performance$pop_fit_max, g = performance$Interval, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'g')
```


### Activation gene coverage

Activation gene coverage analysis.

#### Coverage over time

Activation gene coverage over time.

```{r base-mpe-act-tor-ot, warning=FALSE}
# data for lines and shading on plots
lines = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TOURNAMENT') %>%
  group_by(Interval, Generations) %>%
  dplyr::summarise(
    min = min(pop_act_cov),
    mean = mean(pop_act_cov),
    max = max(pop_act_cov)
  )
ggplot(lines, aes(x=Generations, y=mean, group = Interval, fill = Interval, color = Interval, shape = Interval)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, Generations %% 2000 == 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Activation gene coverage over time')+
  p_theme
```

#### End of 50,000 generations

Activation gene coverage in the population at the end of 50,000 generations.

```{r base-mpe-act-tor-end}
### end of run
filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TOURNAMENT' & Generations == 50000) %>%
  ggplot(., aes(x = Interval, y = pop_act_cov, color = Interval, fill = Interval, shape = Interval)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.3) +
  geom_point(position = position_jitter(height = .05, width = .05), size = 1.5, alpha = 0.5) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_shape_manual(values=SHAPE)+
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_discrete(
    name="Interval"
  ) +
  scale_colour_manual(values = cb_palette_mi) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Final activation gene coverage')+
  p_theme + coord_flip()
```

##### Stats

Summary statistics for activation gene coverage.

```{r base-mpe-act-tor-end-sum}
coverage = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'TOURNAMENT' & Generations == 50000)
coverage %>%
  group_by(Interval) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_act_cov)),
    min = min(pop_act_cov, na.rm = TRUE),
    median = median(pop_act_cov, na.rm = TRUE),
    mean = mean(pop_act_cov, na.rm = TRUE),
    max = max(pop_act_cov, na.rm = TRUE),
    IQR = IQR(pop_act_cov, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of no difference among activation gene coverage.
```{r base-mpe-act-tor-end-kru}
kruskal.test(pop_act_cov ~ Interval, data = coverage)
```

## Lexicase selection

Here we analyze how the different population structures affect standard lexicase selection on the contradictory objectives diagnostic.

### Performance

#### Performance over time

```{r base-lex-mpe-perf, message=FALSE}
lines = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'LEXICASE') %>%
  group_by(Interval, Generations) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )
ggplot(lines, aes(x=Generations, y=mean, group = Interval, fill = Interval, color = Interval, shape = Interval)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, Generations %% 2000 == 0), size = 2.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle("Performance over time") +
  p_theme
```

#### Best performance

Best performance is found throughout in final generation.

```{r base-lex-mpe-per-bst, warning=FALSE}
filter(df_best, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'LEXICASE' & VAR == 'pop_fit_max') %>%
  ggplot(., aes(x = Interval, y = VAL / DIMENSIONALITY, color = Interval, fill = Interval, shape = Interval)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_discrete(
    name="Interval"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi, ) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Best performance')+
  p_theme + coord_flip()
```

##### Stats

Summary statistics for the best performance found.

```{r base-lex-mpe-per-bst-sum}
performance = filter(df_best, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'LEXICASE' & VAR == 'pop_fit_max')
performance$Interval = factor(performance$Interval, levels = c('50','5000','500'))
performance %>%
  group_by(Interval) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(VAL)),
    min = min(VAL, na.rm = TRUE) / DIMENSIONALITY,
    median = median(VAL, na.rm = TRUE) / DIMENSIONALITY,
    mean = mean(VAL, na.rm = TRUE) / DIMENSIONALITY,
    max = max(VAL, na.rm = TRUE) / DIMENSIONALITY,
    IQR = IQR(VAL, na.rm = TRUE) / DIMENSIONALITY
  )
```

Kruskal–Wallis test provides evidence of difference among selection schemes.

```{r base-lex-mpe-per-bst-kru}
kruskal.test(VAL ~ Interval, data = performance)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r base-lex-mpe-per-bst-wil}
pairwise.wilcox.test(x = performance$VAL, g = performance$Interval, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```

#### Final performance

Best performance is found throughout in final generation.

```{r base-lex-mpe-per-end, warning=FALSE}
filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'LEXICASE' & Generations == 50000) %>%
  ggplot(., aes(x = Interval, y = pop_fit_max / DIMENSIONALITY, color = Interval, fill = Interval, shape = Interval)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.2) +
  geom_point(position = position_jitter(width = .1), size = 1.5, alpha = 1.0) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_y_continuous(
    name="Average trait score"
  ) +
  scale_x_discrete(
    name="Interval"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi, ) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Final performance')+
  p_theme + coord_flip()
```

##### Stats

Summary statistics for the best performance is found throughout in final generation..

```{r base-lex-mpe-per-end-sum}
performance = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'LEXICASE' & Generations == 50000)
performance$Interval = factor(performance$Interval, levels = c('50','5000','500'))
performance %>%
  group_by(Interval) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_fit_max)),
    min = min(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    median = median(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    max = max(pop_fit_max / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(pop_fit_max / DIMENSIONALITY, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among selection schemes.

```{r base-lex-mpe-per-end-kru}
kruskal.test(pop_fit_max ~ Interval, data = performance)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r base-lex-mpe-per-end-wil}
pairwise.wilcox.test(x = performance$pop_fit_max, g = performance$Interval, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```

### Activation gene coverage

Activation gene coverage analysis.

#### Coverage over time

Activation gene coverage over time.

```{r base-mpe-act-lex-ot, warning=FALSE}
# data for lines and shading on plots
lines = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'LEXICASE') %>%
  group_by(Interval, Generations) %>%
  dplyr::summarise(
    min = min(pop_act_cov),
    mean = mean(pop_act_cov),
    max = max(pop_act_cov)
  )
ggplot(lines, aes(x=Generations, y=mean, group = Interval, fill = Interval, color = Interval, shape = Interval)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, Generations %% 2000 == 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")

  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette_mi) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Activation gene coverage over time')+
  p_theme
```

#### End of 50,000 generations

Activation gene coverage in the population at the end of 50,000 generations.

```{r base-mpe-act-lex-end}
### end of run
filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'LEXICASE' & Generations == 50000) %>%
  ggplot(., aes(x = Interval, y = pop_act_cov, color = Interval, fill = Interval, shape = Interval)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), scale = 'width', alpha = 0.3) +
  geom_point(position = position_jitter(height = .05, width = .05), size = 1.5, alpha = 0.5) +
  geom_boxplot(color = 'black', width = .2, outlier.shape = NA, alpha = 0.0) +
  scale_shape_manual(values=SHAPE)+
  scale_y_continuous(
    name="Coverage"
  ) +
  scale_x_discrete(
    name="Interval"
  ) +
  scale_colour_manual(values = cb_palette_mi) +
  scale_fill_manual(values = cb_palette_mi) +
  ggtitle('Final activation gene coverage')+
  p_theme + coord_flip()
```

##### Stats

Summary statistics for activation gene coverage.

```{r base-mpe-act-lex-end-sum}
coverage = filter(df_ot, Diagnostic == 'MULTIPATH_EXPLORATION' & `Selection\nScheme` == 'LEXICASE' & Generations == 50000)
coverage$Interval = factor(coverage$Interval, levels = c('50','500','5000'))
coverage %>%
  group_by(Interval) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_act_cov)),
    min = min(pop_act_cov, na.rm = TRUE),
    median = median(pop_act_cov, na.rm = TRUE),
    mean = mean(pop_act_cov, na.rm = TRUE),
    max = max(pop_act_cov, na.rm = TRUE),
    IQR = IQR(pop_act_cov, na.rm = TRUE)
  )
```

Kruskal–Wallis test provides evidence of difference among activation gene coverage.
```{r base-mpe-act-lex-end-kru}
kruskal.test(pop_act_cov ~ Interval, data = coverage)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction on activation gene coverage.

```{r base-mpe-act-lex-end-wil}
pairwise.wilcox.test(x = coverage$pop_act_cov, g = coverage$Interval, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'g')
```